Indicators for Ecosystem Condition in Norway

### 2023-10-04 NDVI_wetland.Rmd
typo

**Western Norway**
```{r west-nvdi-vs-tilstand-ndviw, message=FALSE, warning=FALSE, fig.cap="NDVI agains ecosystm condition for fou wetland ecosystems in W-Norway."}
SentinelNDVI.wetland.train %>%
  filter(region == "Western Norway") %>%
  ggplot(aes(x = tilstand, y = mean)) +
  geom_violin() +
  geom_point(size = 0.7, shape = 16, color = "grey") +
  facet_wrap(~hovedtype)
```
```{r}
summary(model.wetland.cond.Sent.W)$coefficients

>>>>

**Western Norway**
```{r west-nvdi-vs-tilstand-ndviw, message=FALSE, warning=FALSE, fig.cap="NDVI against ecosystem condition for four wetland ecosystems in W-Norway."}
SentinelNDVI.wetland.train %>%
  filter(region == "Western Norway") %>%
  ggplot(aes(x = tilstand, y = mean)) +
  geom_violin() +
  geom_point(size = 0.7, shape = 16, color = "grey") +
  facet_wrap(~hovedtype)
```
```{r}
summary(model.wetland.cond.Sent.W)$coefficients
